---
title: "R Markdown and Leaflet"
author: "Rui Romanini"
date: "14 de junho de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective

The objective is to use the R Markdown and leaflet to plot a map with interactive elements.
For this exercise, I will use open data from Brazil, related to air accidents and total of victims. 
The circle show how many fatal victims happened and the details are showed when
you click in the circle.


## Understanding Data

We can get the data about air accidents in Brazil from CENIPA (Centro de Investigação e Prevenção de Acidentes Aeronáuticos). 

This is the oficial site: http://www2.fab.mil.br/cenipa/

The dataset can be downloaded from 2 urls:

Accidents
https://raw.githubusercontent.com/nosbielcs/opendata_aig_brazil/master/data/oco.csv

Aircraft and number of victims
https://raw.githubusercontent.com/nosbielcs/opendata_aig_brazil/master/data/anv.csv


This datasets contain accidents ocurred between 2006 and 2015. I did select the 10 worst accidents, with greater number of victims.


### Brazil Air Accidents

The map below contain the 10 worst air accidents ocurred in Brazil between 2006 and 2015.

When clicked, the Marker will show the total of victims in the accident.

If click Zoom in the map will show the markers, with details.
If click Zoom out, the map will group the markers in several clusters, showing the total of accidents in the cluster

The circle size show the ammount of victims in the accident.

```{r,echo=FALSE}

brasilAccidents <-data.frame(
  lat= c(-23.5674,-10.7444,-22.6444,-16.4406,-23.4917,-16.5408,-3.2592,-0.8669,-21.8000,-3.0411),
  lng = c(-46.5704,-53.5203,-42.3203,-52.0042,-46.6444,-39.1078,-60.6719,-52.6436,-43.3869,-60.0506),
  vitim = c(199,154,19,8,8,14,24,10,8,7))


```


```{r,echo=FALSE}
library(leaflet)

brasilAccidents %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = paste(as.character(brasilAccidents$vitim), "victims"),clusterOptions =markerClusterOptions())%>%
  addCircles(weight=1,radius = brasilAccidents$vitim * 500)
```


## Conclusion

This kind of visualization allow to search for details in the accident, grouping clusters, check 
the exact place of accident or see the number of victims.




